---
title: "Alcohol vs Seat choice"
author: "LuisJovelPalacios"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

I noticed that the number of people siting in the middle is the higest (89) between the number of people sitting in the front (40) and the back (36). however the standard devision of the people sitting in the back is the highest (12.580471) compared to the people in the front (3.806013) and in the middle (6.225381).  
  
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

 when looking at the p-value which was about 0.000116 I noticed that it is really small and that it is telling me that there is a big statistical difference between the values. 
 
```{r}
plot(TukeyHSD(model1))
```

Looking at the 95% confidence level. I saw the confidence interval of the front-back, and middle-front seats, with 0 indicating if the lines are significantly diffrent or not. when i observed the results i noticed that the front-back and middle back are indeed significatly diffrent since 0 doesnt go through their confidence intervals. however for the middle front seat 0 does go threw the confidence intreval and so indicating that the is no significat diffrence between them.

## Conclusions

what i learned in todays class is that looking at numerical catrgorical data but the difrence this time is that there are more diffrenet categories and so i used my helper file and went down to one way anova to help me solve this assignemnt it is more complicated than the last numerical categories data i used.
